Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-13 paper.tex
Hyphenate lift-to-drag
Typo

\caption{Airfoil maximum lift to drag ratio versus Reynolds number, from
    \cite{McMasters1980}.}

@@

Experiments were performed in a turbine test bed specifically designd for
cross-flow turbines. The turbine model used in this study was the UNH Reference
Vertical Axis Turbine (RVAT), which was designed to be a generic case for
numerical model testing, similar to the Sandia National Labs/US Department of
Energy RM2 River Turbine \cite{Neary2014}, but with higher solidity, or blade
chord to radius ratio.

>>>>

\caption{Airfoil maximum lift-to-drag ratio versus Reynolds number, from
    \cite{McMasters1980}.}

@@

Experiments were performed in a turbine test bed specifically designed for
cross-flow turbines. The turbine model used in this study was the UNH Reference
Vertical Axis Turbine (RVAT), which was designed to be a generic case for
numerical model testing, similar to the Sandia National Labs/US Department of
Energy RM2 River Turbine \cite{Neary2014}, but with higher solidity, or blade
chord to radius ratio.
